How is the Brazilian Amazon constructed as a problem at different levels? Amazonian

### 2022-02-11 20220210_Draft.Rmd
#polishedthedictionaryabit #randomsamplefromAS_long

sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|ocupar|forcas armadas|militar|fronteir|patrimonio|nacional|defesa|exercito|dono|nossa")

development <- ("estrada|rodovia|hidroeletrica|desenvolv|balbina|itaipu|incentivos fiscais| integra|zona franca|transamazonica|madeira|porto|madeireira|produz|energia|agro|agri")

conservation <- ("preserv|conserv|determinacao|povos indigenas|indigenas|direitos humanos|areas demarcadas|queimada|sustentav|meio ambiente|florest|cooperaçao|protecao|proteg")

# Create a variable for each and count matches
Amazon_speeches$sovereignty <- stringr::str_count(Amazon_speeches$text, paste0("(?i)", sovereignty))
Amazon_speeches$development <- stringr::str_count(Amazon_speeches$text, paste0("(?i)", development))
Amazon_speeches$conservation <- stringr::str_count(Amazon_speeches$text, paste0("(?i)", conservation))
Amazon_speeches$other <- ifelse(Amazon_speeches$sovereignty == 0 & Amazon_speeches$development == 0 & 
                                  Amazon_speeches$conservation == 0, 1, 0)
# Notice we count each match here, is that what we want? If not, see code chunk below.
# Visulaize totals
tibble::tibble(Sovereignty = sum(Amazon_speeches$sovereignty),
               Development = sum(Amazon_speeches$development),
               Conservation = sum(Amazon_speeches$conservation),
               Other = sum(Amazon_speeches$other))
#dat <- Amazon_speeches %>% sample_frac(.1)
#dat <- apply(dat,2,as.character)
#write.csv(dat, file = "random_sample.csv")
```

>>>>

sovereignty <- ("amazonia e brasileira|amazonia e nossa|soberania|interesse estrangeiro|ocupar|forcas armadas|patrimonio nacional|defesa|exercito|donoo|internacionalizar")

development <- ("estrada|rodovia|hidroeletrica|desenvolv|balbina|itaipu|incentivos fiscais|integra|zona franca|transamazonica|madeira|porto|madeireira|energia|estimulo|banco|hidreletrica|convenio|sede|fome|saude|hospital|escola|saneamento|social")

conservation <- ("preserv|conserv|determinacao|povos indigenas|demarcar|queimada|sustentav|meio ambiente|florest|protecao|proteg|renovavel|garantias ambientais|garantia ambiental|reduzir desmatamento|combate ao desmatamento|combater desmatamento|baixo carbono|limpa|direitosambientais")

# Create a variable for each and count matches
Amazon_speeches$sovereignty <- stringr::str_count(Amazon_speeches$text, paste0("(?i)", sovereignty))
Amazon_speeches$development <- stringr::str_count(Amazon_speeches$text, paste0("(?i)", development))
Amazon_speeches$conservation <- stringr::str_count(Amazon_speeches$text, paste0("(?i)", conservation))
Amazon_speeches$other <- ifelse(Amazon_speeches$sovereignty == 0 & Amazon_speeches$development == 0 & 
                                  Amazon_speeches$conservation == 0, 1, 0)

# Notice we count each match here, is that what we want? If not, see code chunk below.
# Visulaize totals
tibble::tibble(Sovereignty = sum(Amazon_speeches$sovereignty),
               Development = sum(Amazon_speeches$development),
               Conservation = sum(Amazon_speeches$conservation),
               Other = sum(Amazon_speeches$other))
#dat <- Amazon_speeches %>% sample_frac(.1)
#dat <- apply(dat,2,as.character)
#write.csv(dat, file = "random_sample.csv")
```
